{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed, Object Tracking

### 2017-06-16 bmvc_review.tex
Text Cleaned

We also evaluate the performances of the different combinations of the
proposed correlation filters and compare them to the {\it E}nKCF as shown in table~\ref{table:Comparison_to_LCT}.  
By using three KCFs ( $R_{t}^{L}$, $R_{t}^{S}$, $R_{s}$) in {\it E}nKCF,
we can achieve higher accuracy than using $R_{s}$ and $R_{t}^{L}$ or
$R_{t}^{S}$ with similar run-time performance. On the other hand, we
employ $R_{s}$ and $R_{t}^{L}$ or $R_{t}^{S}$ and run them in every frame in a similar way
to the multiple correlation filter framework of the LCT tracker \cite{ma2015long}. Running another filter, $R_{t}^{L}$ or
$R_{t}^{S}$, in the {\it E}nKCF framework not only boosts run-time performance but also increases
accuracy. Finally, we run  $R_{L}$, $R_{t}^{S}$ and $R_{s}$ in every frame in the in the given order. 
$R_{t}^{S}$ uses the translation estimation given by
$R_{t}^{L}$ to update translation and finally $R_{s}$ uses the final
translation estimation given by $R_{t}^{S}$ to update the
scale. Interestingly, running two complementary translation filter
results in significant improvement at the cost of decreased run-time
performance. In conclusion, running two complementary translation
filter and a scale filter in the {\it E}nKCF framework not only
provides high speed but also more accurate tracker than the baseline
methods having one translation and one scale filter.
\begin{table}[!h]
\smaller
\begin{center}
\color{green}--- Best \hspace{.15\linewidth}\color{red}--- $2^{nd}$ Best \hspace{.15\linewidth}\color{blue}--- $3^{th}$ Best \color{black}\\
\resizebox{\textwidth}{!}{\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
\hline
Method & {\it E}nKCF & $R_{t}^{S}$+$R_{t}^{L}$+$R_{s}$ & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & $R_{t}^{L}$* & $R_{t}^{S}$* & $R_{t}^{L}$+$R_{s}$* & $R_{t}^{S}$+$R_{s}$* & $R_{t}^{L}+R_{t}^{S}$+$R_{s}$* \\
\hline\hline
Pr. ($20$px) & \color{blue}53.9 & 48.93 &52.41 & 48.10 & 51.88 & 51.29 & \color{red} 55.85 & 52.14 & \color{green}58.16 \\
SR ($50\%$) & \color{red} 40.2 & 36.75 & 38.23 & 36.04 & 35.12 & 34.43 & \color{blue}39.89 & 38.51 & \color{green}41.58 \\
FPS & \color{red} 416 & \color{blue}412 & 370 & \color{green}425 & 365 & 384 & 135 & 151 & 99 \\
\hline
\end{tabular}}
\end{center}
\caption{Evaluations of the different combinations of the proposed
  KCFs in UAV123 dataset. The $2^{nd}$ method swaps the order of
  $R_{t}^{L}$ and $R_{t}^{S}$ (fig.~\ref{Workflows}). The $3^{th}$
  method removes $R_{t}^{S}$ and replaces with $R_{t}^{L}$ whereas the
  $3^{th}$ one removes $R_{t}^{L}$. The methods denoted with "*" run
  the filters in every frame in the listed order. The LCT tracker
  \cite{ma2015long} runs a translation and scale filter in every frame
  (similar to $6^{th}$ method) and couples a re-detection method to
  perform long-term tracking at $\approx30$ fps.}
\label{table:Comparison_to_LCT}
\end{table}

Finally, on the $UAV123$ dataset, we compare the {\it E}nKCF with particle filter and without particle filter. To do so, we use the 50 video sequences with no abrupt camera motion as annotated by the authors. Also, we add noise, drawn from a uniform distribution ($[-20,20]$), to the translation estimations of the KCFs to further evaluate the robustness of particle filter. In this settings, the {\it E}nKCF with particle filter achieves $51.98\%$ precision ($20$px), outperforming the baseline {\it E}nKCF by $6.32\%$.  In conclusion, the proposed particle filter can be a useful tool in {\it E}nKCF framework with the removal of global camera motion.

>>>>

We also evaluate the performances of different combinations of the proposed correlation filters and 
compare them to {\it E}nKCF as shown in table~\ref{table:Comparison_to_LCT}.  
By using three KCFs ( $R_{t}^{L}$, $R_{t}^{S}$, $R_{s}$) in {\it E}nKCF,
we can achieve higher accuracy than using $R_{s}$ and $R_{t}^{L}$ or
$R_{t}^{S}$ with similar run-time performance. On the other hand, we
employ $R_{s}$ and $R_{t}^{L}$ or $R_{t}^{S}$ and run them in every frame in a similar way
to the multiple correlation filter framework of the LCT tracker \cite{ma2015long}. Running another filter, $R_{t}^{L}$ or
$R_{t}^{S}$, in the {\it E}nKCF framework not only boosts run-time performance but also increases
accuracy. Finally, we run  $R_{L}$, $R_{t}^{S}$ and $R_{s}$ in every frame in the in the given order. 
$R_{t}^{S}$ uses the translation estimation given by
$R_{t}^{L}$ to update translation and finally $R_{s}$ uses the final
translation estimation given by $R_{t}^{S}$ to update the
scale. Interestingly, running two complementary translation filter
results in significant improvement at the cost of decreased run-time
performance. In conclusion, running two complementary translation
filter and a scale filter in the {\it E}nKCF framework not only
provides high speed but also more accurate tracker than the baseline
methods having one translation and one scale filter.
\begin{table}[!h]
\smaller
\begin{center}
\color{green}--- Best \hspace{.15\linewidth}\color{red}--- $2^{nd}$ Best \hspace{.15\linewidth}\color{blue}--- $3^{th}$ Best \color{black}\\
\resizebox{\textwidth}{!}{\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
\hline
Method & {\it E}nKCF & $R_{t}^{S}$+$R_{t}^{L}$+$R_{s}$ & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & $R_{t}^{L}$* & $R_{t}^{S}$* & $R_{t}^{L}$+$R_{s}$* & $R_{t}^{S}$+$R_{s}$* & $R_{t}^{L}+R_{t}^{S}$+$R_{s}$* \\
\hline\hline
Pr. ($20$px) & \color{blue}53.9 & 48.93 &52.41 & 48.10 & 51.88 & 51.29 & \color{red} 55.85 & 52.14 & \color{green}58.16 \\
SR ($50\%$) & \color{red} 40.2 & 36.75 & 38.23 & 36.04 & 35.12 & 34.43 & \color{blue}39.89 & 38.51 & \color{green}41.58 \\
FPS & \color{red} 416 & \color{blue}412 & 370 & \color{green}425 & 365 & 384 & 135 & 151 & 99 \\
\hline
\end{tabular}}
\end{center}
\caption{Evaluations of the different combinations of the proposed
  KCFs in UAV123 dataset. The particle filter is decoupled from all the methods for fair comparison. 
  The $2^{nd}$ method swaps the order of
  $R_{t}^{L}$ and $R_{t}^{S}$ (fig.~\ref{Workflows}). The $3^{th}$
  method removes $R_{t}^{S}$ and replaces with $R_{t}^{L}$ whereas the
  $3^{th}$ one removes $R_{t}^{L}$. The methods denoted with "*" run
  the filters in every frame in the listed order. The LCT tracker
  \cite{ma2015long} runs a translation and scale filter in every frame
  (similar to $6^{th}$ method) and couples a re-detection method to
  perform long-term tracking at $\approx30$ fps.}
\label{table:Comparison_to_LCT}
\end{table}

Finally, on the $UAV123$ dataset, we compare the {\it E}nKCF with particle filter to the one without particle filter. To do so, we use 50 sequences labeled as no abrupt camera motion in the dataset. To evaluate the robustness of particle filter, we add noise, drawn from a uniform distribution ($[-20,20]$), to the translation estimations of the KCFs. In these settings, the {\it E}nKCF with particle filter achieves $51.98\%$ precision ($20$px), outperforming the baseline {\it E}nKCF by $6.32\%$.  In conclusion, with the removal of global camera motion, the integration of particle filter into the {\it E}nKCF as shown in fig.~\ref{Workflows} can further improve the results.
